BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-07-31 main.tex
Layout
Update metadata

%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf, % <-- Not sure if this should be enabled
]{ceurart}

@@

\conference{BPM 2024: Demos and Resources, September 01-06, 2024, Krakow, PL}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.8\linewidth]{images/counter-example}
	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
	\label{fig:counterexample}
\end{figure*}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quick-fix}
	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
	\label{fig:quick-fixes}
\end{figure*}

>>>>

%% hf: enable header and footer.
\documentclass[
twocolumn, % TODO: has to be one col
% hf, % <-- Not sure if this should be enabled
]{ceurart}

@@

\conference{Proceedings of the Best BPM Dissertation Award, Doctoral Consortium, and Demonstrations \& Resources Forum co-located with 22nd International Conference on Business Process Management (BPM 2024), Krakow, Poland, September 1st to 6th, 2024.}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.82\linewidth]{images/counter-example}
	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
	\label{fig:counterexample}
\end{figure*}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.82\linewidth]{images/quick-fix}
	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
	\label{fig:quick-fixes}
\end{figure*}
